---
title: "Cathepsins file"
output:
  pdf_document: default
  html_notebook: default
---

```{r}

#install.packages("readxl")
#install.packages("imager")
#devtools::install_bitbucket("graumannlabtools/multipanelfigure")

# install.packages("BiocManager")
# BiocManager::install("EBImage")

#install.packages('readbitmap')
```


```{r}
library(ggplot2)
library(dplyr)
library(gapminder)
library(ggthemes)
library("readxl")
library(tidyverse)
library(imager)
library("EBImage")
library(plotly)
```

#### Read the excel file
```{r}
Cathepsins <- read_excel("Results_Cathepsins.xlsx")
```


# Cathepsins Fluorescent Intensity


### Now we plot a Grouped graph for Cathepsin B fluorescent intensity levels
```{r}
 
# Grouped

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin B") %>%
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin B_Int", 
              title = "Cathepsin B levels") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)
      
      
```


## Now we zoom into a specific Y-axis range
```{r}
 
# Grouped

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin B") %>%
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin B_Int", 
              title = "Cathepsin B levels") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      coord_cartesian(ylim = c(155, 165)) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)
      

```




## Filtered data

### Now we plot a Grouped graph for only specific columns that we want for Cathepsin B fluorescent intensity levels
```{r}
 

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin B") %>%
      filter(Treatment == "GAf" | Treatment == "GAs" | Treatment == "PAs" | Treatment == "Unt") %>% 
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin B_Int", 
              title = "Cathepsin B levels") +
      scale_fill_manual(values = c("#003f5c", "#7a5195",    
                                   "#ef5675", "#ffa600")) +
      coord_cartesian(ylim = c(155, 165)) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```





### Now we plot a Grouped graph for Cathepsin B Area of signal
```{r}
 
# Grouped

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin B") %>%
      ggplot() +
      geom_bar(aes(y=Area_of_Signal, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin B_Area of signal", 
              title = "Cathepsin B Area") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```


### Now we plot a Grouped graph for only specific columns that we want for Cathepsin B Area

```{r}



# Grouped

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin B") %>%
      filter(Treatment == "GAf" | Treatment == "GAs" | Treatment == "PAs" | Treatment == "Unt") %>% 
      ggplot() +
      geom_bar(aes(y=Area_of_Signal, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin B_Area of signal", 
              title = "Cathepsin B Area") +
      scale_fill_manual(values = c("#003f5c", "#7a5195",    
                                   "#ef5675", "#ffa600")) +
      #coord_cartesian(ylim = c(155, 165)) +
      #theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)



```











### Now we plot a Grouped graph for Cathepsin D fluorescent intensity levels
```{r}
# Group 

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin D") %>%
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin D_Int", 
              title = "Cathepsin D levels") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      #coord_cartesian(ylim = c(160, 185)) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)
      


```



### Now we plot a Grouped graph for Cathepsin D fluorescent intensity levels for a specific range
```{r}
# Group 

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin D") %>%
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin D_Int", 
              title = "Cathepsin D levels") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      coord_cartesian(ylim = c(165, 185)) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)
      


```



## Filtered data

### Now we plot a Grouped graph for only specific columns that we want for Cathepsin D fluorescent intensity levels
```{r}
 
# Grouped


p <- Cathepsins %>% 
      filter(Condition == "Cathepsin D") %>%
      filter(Treatment == "GAf" | Treatment == "GAs" | Treatment == "PAs" | Treatment == "Unt") %>% 
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin D_Int", 
              title = "Cathepsin D levels") +
      scale_fill_manual(values = c("#003f5c", "#7a5195",    
                                   "#ef5675", "#ffa600")) +
      #coord_cartesian(ylim = c(155, 165)) +
      #theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```





### Now we plot a Grouped graph for Cathepsin D Area of signal
```{r}
 
# Grouped


p <- Cathepsins %>% 
      filter(Condition == "Cathepsin D") %>%
      ggplot() +
      geom_bar(aes(y=Area_of_Signal, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin D_Area of signal", 
              title = "Cathepsin D Area") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)

```


### Now we plot a Grouped graph for only specific columns that we want for Cathepsin D Area

```{r}
 # Grouped

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin D") %>%
      filter(Treatment == "GAf" | Treatment == "GAs" | Treatment == "PAs" | Treatment == "Unt") %>% 
      ggplot() +
      geom_bar(aes(y=Area_of_Signal, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin D_Area of signal", 
              title = "Cathepsin D Area") +
      scale_fill_manual(values = c("#003f5c", "#7a5195",    
                                   "#ef5675", "#ffa600")) +
      #coord_cartesian(ylim = c(155, 165)) +
      #theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```



















### Now we plot a Grouped graph for Cathepsin L fluorescent intensity levels
```{r}
 
# Grouped
p <- Cathepsins %>% 
      filter(Condition == "Cathepsin L") %>%
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin L_Int", 
              title = "Cathepsin L levels") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      #coord_cartesian(ylim = c(155, 185)) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```



## Filtered data

### Now we plot a Grouped graph for only specific columns that we want for Cathepsin L fluorescent intensity levels
```{r}
 
# Grouped
p <- Cathepsins %>% 
      filter(Condition == "Cathepsin L") %>%
      ggplot() +
      geom_bar(aes(y=Fluo_Int, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin L_Int", 
              title = "Cathepsin L levels") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      coord_cartesian(ylim = c(155, 180)) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```





### Now we plot a Grouped graph for Cathepsin L Area of signal
```{r}
 
# Grouped

p <- Cathepsins %>% 
      filter(Condition == "Cathepsin L") %>%
      ggplot() +
      geom_bar(aes(y=Area_of_Signal, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin L_Area of signal", 
              title = "Cathepsin L Area") +
      scale_fill_manual(values = c("#003f5c", "#003f5c", "#7a5195", "#7a5195",   
                                    "#ef5675", "#ef5675", "#ffa600", "#ffa600")) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)


```


### Now we plot a Grouped graph for only specific columns that we want for Cathepsin L Area

```{r}
 # Grouped
p <- Cathepsins %>% 
      filter(Condition == "Cathepsin L") %>%
      filter(Treatment == "GAf" | Treatment == "GAs" | Treatment == "PAs" | Treatment == "Unt") %>% 
      ggplot() +
      geom_bar(aes(y=Area_of_Signal, x=Treatment, fill= Treatment),
               position="dodge", stat = "summary", fun.y = "mean") + 
      labs(x = "", y = "Cathepsin L_Area of signal", 
              title = "Cathepsin L Area") +
      scale_fill_manual(values = c("#003f5c", "#7a5195",    
                                   "#ef5675", "#ffa600")) +
      #coord_cartesian(ylim = c(155, 165)) +
      #theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 

      ggplotly(p)
      

```



